---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bbd

<!-- badges: start -->
[![R-CMD-check](https://github.com/daviddalpiaz/bbd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/daviddalpiaz/bbd/actions)
<!-- badges: end -->

The `bbd` package is an [lightweight package](https://www.tinyverse.org/) that contains functions to facilitate the collection of **b**ase**b**all **d**ata from various sources online. **This package is currently experimental.** All function interfaces are liable to change without notice.

For a mature and feature rich baseball data package, consider [`baseballr`](https://github.com/BillPetti/baseballr).

## Installation

You can install the development version of `bbd` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("daviddalpiaz/bbd")
```

## Example

The most basic usage of `bbd` is collecting [Statcast data](https://baseballsavant.mlb.com/statcast_search) for all games played between two dates, inclusive.

```{r ws-example, eval = FALSE}
library(bbd)
ws_2022 = statcast(start = "2022-10-28", end = "2022-11-05")
```

```{r sc-example, echo = FALSE}
library(bbd)
sc = statcast(start = "2022-10-28", end = "2022-10-28")
statcast_info = data.frame(
  "Variable Name" = names(sc),
  "Variable Type" = sapply(sc, typeof),
  check.names = FALSE
)
```

### Statcast Variables

By default, `bbd` attempts to be un-opinionated, and thus returns a data frame containing the exact variables returned by the Statcast API. Notice that `pitcher` and `fielder_2` variables are duplicated.

```{r sc-info-table, echo = FALSE}
knitr::kable(statcast_info)
```

The `statcast()` function provides arguments that allow for some opinionated processing. Check the documentation for deatils of this processing. Most importantly, functionality to obtain both batter *and* pitcher names is included.

```{r, eval = FALSE}
ws_2022_processed = statcast(
  start = "2022-10-28",
  end = "2022-11-05",
  process = TRUE,
  names = TRUE
)
```

```{r sc-example-proc, echo = FALSE}
library(bbd)
sc_proc = statcast(
  start = "2022-10-28",
  end = "2022-11-05",
  process = TRUE,
  names = TRUE
)
statcast_info_proc = data.frame(
  "Variable Name" = names(sc),
  "Variable Type" = sapply(sc, typeof),
  check.names = FALSE
)
```

```{r sc-info-table-proc, echo = FALSE}
knitr::kable(statcast_info_proc)
```
