---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bbd

<!-- badges: start -->
[![R-CMD-check](https://github.com/daviddalpiaz/bbd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/daviddalpiaz/bbd/actions)
<!-- badges: end -->

The `bbd` package is a [lightweight package](https://www.tinyverse.org/) that contains functions to facilitate the collection of baseball data from various sources online. **This package is currently experimental.** All function interfaces are liable to change without notice.

For a mature and feature rich baseball data package, consider [`baseballr`](https://github.com/BillPetti/baseballr).

## Installation

You can install the development version of `bbd` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("daviddalpiaz/bbd")
```

## Example

The most basic usage of `bbd` is collecting [Statcast data](https://baseballsavant.mlb.com/statcast_search) for all games played between two dates, inclusive.

```{r example}
library(bbd)
ws_2022 = statcast(start = "2022-10-28", end = "2022-11-05")
```

```{r, echo = FALSE}
sc = statcast(start = "2022-10-28", end = "2022-10-28")
statcast_info = data.frame(
  "Variable Name" = names(sc),
  "Variable Type" = sapply(sc, typeof),
  check.names = FALSE
)
```

### Statcast Variables

```{r, echo = FALSE}
knitr::kable(statcast_info)
```
