---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bbd

<!-- badges: start -->
[![R-CMD-check](https://github.com/daviddalpiaz/bbd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/daviddalpiaz/bbd/actions)
<!-- badges: end -->

The `bbd` package contains functions that facilitating collecting baseball data from various sources online. **This packages is currently experimental.** All function interfaces are liable to change.

For a mature and feature rich baseball data package, consider [`baseballr`](https://github.com/BillPetti/baseballr).

## Installation

You can install the development version of `bbd` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("daviddalpiaz/bbd")
```

## Example

```{r, echo = FALSE}
options("datatable.print.topn" = 5)
options("datatable.print.nrows" = 10)
options("datatable.print.class" = TRUE)
options("datatable.print.trunc.cols" = TRUE)
options("datatable.print.keys" = TRUE)
```

The most basic usage of **`bbd`** is collecting [statcast data](https://baseballsavant.mlb.com/statcast_search) for all games played on a particular day.

```{r example}
library(bbd)
get_statcast_day(date = "2021-11-02")[, 1:5]
```
